---
title: "Lennox_Panel_Model"
author: "Data Wranglers"
date: "March 28, 2019"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(plm)
library(recipes)
library(car)
library(zoo)
```

## Importing data and initial cleaning



```{r cars}
lennox<-read_csv('Final_Model_Data_reduced_store.csv')

lennox<-lennox%>%
  filter(!Sales==0)

lennox$Trade_Area_Size[lennox$Trade_Area_Size=="small Market"]="Small Market"

lennox$FISCAL_YEAR_PERIOD=as.yearmon(lennox$FISCAL_YEAR_PERIOD, format = '%m/%d/%Y')

head(lennox)

```

## Data Transformations

You can also embed plots, for example:

```{r pressure, echo=FALSE}

lennox_rec <- recipe(Sales ~ ., data = lennox) %>%
  step_log(Sales,Foottraffic,Total_Population,Total_HH)%>%
  prep(data = lennox,retain = TRUE)

lennox_rec_std <- recipe(Sales ~ ., data = lennox) %>%
  step_log(Sales,Foottraffic,Total_Population,Total_HH)%>%
  step_center(all_numeric(), -all_outcomes()) %>%
  step_scale(all_numeric(), -all_outcomes())%>%
  prep(data = lennox,retain = TRUE)

lennox_tbl <-bake(lennox_rec, newdata = lennox)
lennox_tbl_std <-bake(lennox_rec_std, newdata = lennox)

lennox_panel<-pdata.frame(lennox_tbl,index = c("Plant","FISCAL_YEAR_PERIOD"))
lennox_panel_std<-pdata.frame(lennox_tbl_std,index = c("Plant","FISCAL_YEAR_PERIOD"))

```

## Data models

Panel data models like Fixed Effects and Random Effects allows us to remove unobserved Heterogenity in the model and therefore more accurate estimates of variable effects than OLS model  

```{r}
form=Sales~Store_Size+Foottraffic+I(Foottraffic^2)+PhoneCalls+MktgAdopt+WCMTDtoQuota+I(WCMTDtoQuota^2)+VOC+PartsSuppliesMTDtoQuota+WCMTDtoQuota*Store_Size

#OLS model
plmpooled <- plm(form, data=lennox_panel, model = "pooling")
summary(plmpooled)

#Fixed Effect Model
plmwithin <- plm(form, data=lennox_panel, model = "within")
summary(plmwithin)

#Random Effect Model
plmrandom <- plm(form, data = lennox_panel, model = "random")
summary(plmrandom)
```


## variable Comparision

For variable comparision, we can use standardised variables so each variable is in similar scale

```{r}

#OLS model
plmpooled <- plm(form, data=lennox_panel_std, model = "pooling")
summary(plmpooled)

#Fixed Effect Model
plmwithin <- plm(form, data=lennox_panel_std, model = "within")
summary(plmwithin)

#Random Effect Model
plmrandom <- plm(form, data = lennox_panel_std, model = "random")
summary(plmrandom)

```


## Plots to clear estimated coefficients

```{r}
ggplot(data=lennox,aes(x=WCMTDtoQuota,y=Sales, color=Store_Size))+
  geom_point()+
  geom_smooth(se = FALSE)

ggplot(data=lennox,aes(x=MktgAdopt,y=Sales, color=Store_Size))+
  geom_point()+
  geom_smooth(se = FALSE)
```


#Prediction Model

Inorder to predict sales we create a OLS model using the formula established since prediction doesnot require accurate estimators.

```{r}

lennox_train<-read_csv('Final_Model_Data_reduced.csv')

lennox_train<-lennox_train%>%
  filter(!Sales==0)

lennox_train$Trade_Area_Size[lennox_train$Trade_Area_Size=="small Market"]="Small Market"

lennox_train$FISCAL_YEAR_PERIOD=as.yearmon(lennox_train$FISCAL_YEAR_PERIOD, format = '%m/%d/%Y')

lennox_rec_train <- recipe(Sales ~ ., data = lennox_train) %>%
  step_log(Sales,Foottraffic,Total_Population,Total_HH)%>%
  step_center(all_numeric(), -all_outcomes()) %>%
  step_scale(all_numeric(), -all_outcomes())%>%
  prep(data = lennox_train,retain = TRUE)

lennox_train_tbl <-bake(lennox_rec_train, newdata = lennox_train)

head(lennox_train_tbl)

form_new=Sales~Plant+Category+FISCAL_YEAR_PERIOD+Store_Size+Foottraffic+I(Foottraffic^2)+PhoneCalls+MktgAdopt+WCMTDtoQuota+I(WCMTDtoQuota^2)+VOC+PartsSuppliesMTDtoQuota+WCMTDtoQuota*Store_Size

lmmod<-lm(form_new, data=lennox_train_tbl)
summary(lmmod)

```



##Prediction Validation Set

```{r}

lennox_valid<-read_csv('Final_Model_Data_validation.csv')
lennox_valid$Trade_Area_Size[lennox_valid$Trade_Area_Size=="small Market"]="Small Market"
lennox_valid$FISCAL_YEAR_PERIOD=as.yearmon(lennox_valid$FISCAL_YEAR_PERIOD, format = '%m/%d/%Y')

lennox_valid_tbl <-bake(lennox_rec_train, newdata = lennox_valid)

lennox_valid_tbl<-lennox_valid_tbl%>%
  filter(!is.na(lennox_valid_tbl$Plant))

lennox_valid_tbl$Salespred<-predict(lmmod,newdata=lennox_valid_tbl)

head(lennox_valid_tbl)

lennox_valid_tbl$resid<-lennox_valid_tbl$Sales-lennox_valid_tbl$Salespred

colnames(lennox_valid_tbl)[colSums(is.na(lennox_valid_tbl))>0]

print(paste("R2 Validation -->",as.character(1-var(lennox_valid_tbl$resid)/var(lennox_valid_tbl$Sales))))


write.csv(lennox_valid_tbl,"Final_Model_Data_validation_pred.csv")

```


##Predicting Test Set

```{r}
lennox_Test<-read_csv('Final_Model_Data_Test.csv')
lennox_Test$Trade_Area_Size[lennox_Test$Trade_Area_Size=="small Market"]="Small Market"
lennox_Test$FISCAL_YEAR_PERIOD=as.yearmon(lennox_Test$FISCAL_YEAR_PERIOD, format = '%m/%d/%Y')

lennox_Test_tbl <-bake(lennox_rec_train, newdata = lennox_Test)

lennox_Test_tbl<-lennox_Test_tbl%>%
  filter(!is.na(lennox_Test_tbl$Plant))

lennox_Test_tbl$Salespred<-predict(lmmod,newdata=lennox_Test_tbl)

head(lennox_Test_tbl)


colnames(lennox_Test_tbl)[colSums(is.na(lennox_Test_tbl))>0]

write.csv(lennox_Test_tbl,"Final_Model_Data_Test_pred.csv")
```


